Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ \smaller \textbf{{Istanbul version \YellowPaperVersionNumber}}

### 2021-06-11 Paper.tex
Block reward corrections

\hypertarget{block_reward_R__block}{}\linkdest{R__block}We define the block reward in Ether:
\begin{equation}
\text{Let} \quad R_{\mathrm{block}} = 10^{18} \times \begin{cases}
5 &\text{if}\ H_{\mathrm{i}} < 4370000 \\
3 &\text{if}\ H_{\mathrm{i}} < 7280000 \\
2 &\text{otherwise}
\end{cases} \\
\end{equation}

>>>>

\hypertarget{block_reward_R__block}{}\linkdest{R__block}We define the block reward in Wei:
\begin{equation}
R_{\mathrm{block}} = 10^{18} \times \begin{cases}
5 &\text{if}\ H_{\mathrm{i}} < 4370000 \\
3 &\text{if}\ 4370000 \leqslant H_{\mathrm{i}} < 7280000 \\
2 &\text{if}\ H_{\mathrm{i}} \geqslant 7280000 \\
\end{cases} \\
\end{equation}
